Approximation as Differentiation

### 2025-05-05 appendix/notes/auto-diff.tex
Fix morphisms in Fam(FinVect).
Move LatGal and FinVect to after section on biproducts/semi-additive categories.

For any $(f, \partial f): (X, \{V_x\}_{x \in X}) \to (Y, \{W_y\}_{y \in Y})$ and $(g, \partial g): (Y,
\{W_y\}_{y \in Y}) \to (Z, \{U_z\}_{z \in Z})$ we have:
\begin{itemize}
\item $\partial f: \{V_x\}_{x \in X} \to \{W_{f(x)}\}_{x \in X}$;
\item $\Fam(g, \FinVect)(\partial g): \Fam(g, \FinVect)(\{W_y\}_{y \in Y}) \to \Fam(g, \FinVect)(\{Z_{g(y)}\}_{y \in Y})$.
\end{itemize}

>>>>

\noindent Also recall that $\Fam(f, \FinVect)$ for any function $f: X \to Y$ is the reindexing functor
$\reindex{-}{f}: \Fam(Y, \FinVect) \to \Fam(X, \FinVect)$ which sends any family of morphisms $\{g_y\}_{y \in
Y}$ to $\{g_{f(x)}\}_{x \in X}$. Then for any $(f, \partial f): (X, \{V_x\}_{x \in X}) \to (Y, \{W_y\}_{y \in
Y})$ and $(g, \partial g): (Y, \{W_y\}_{y \in Y}) \to (Z, \{U_z\}_{z \in Z})$ we have:
\begin{itemize}
\item $\partial f_x: V_x \to W_{f(x)}$ for any $x \in X$;
\item $\reindex{(\partial g_x)}{f}: \{W_{f(x)}\}_{x \in X} \to \{Z_{g(f(x))}\}_{x \in X}$.
\end{itemize}
